Preregistration

### 2021-04-26 preregistration.Rmd
externalise hash

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 2
  nmin: 100
  nmax: 300
  nstep: 100
  seed: 1234
repro:
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
    - future.batchtools
    - slider
    - patchwork
    - svglite
  scripts:
    - R/simulation.R
---

@@

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "4203854848ad0cc5d2f848c44b70815d"){
  warning("Mismatch between original and current simulations!
Checksum now is:\n    '", checksum, "'")
}
```

>>>>

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 2
  nmin: 100
  nmax: 300
  nstep: 100
  seed: 1234
repro:
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
    - future.batchtools
    - slider
    - patchwork
    - svglite
  scripts:
    - R/simulation.R
    - R/hash.R
---

@@

```{r hash}
```
